---
title: "Lab 03 - Nobel laureates"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises 1

The dataset contains `r nrow(nobel)` observations and `r ncol(nobel)` variables. Each row represents a single Nobel Prize award received in a given year and category. 

```{r filter-data,message=FALSE}
nobel_living <- nobel %>%
  filter(
    is.na(died_date),
    !is.na(country),
    gender != "org")
```

After applying these filters, the resulting dataset contains `r nrow(nobel_living)` observations.



### Exercise 2

```{r judge—USA—or—Not}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
```
```{r tring-to-not-annoy-an-economist}
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```


```{r plot-us-based-by-category}
nobel_living_science %>%
  ggplot(aes(x = country_us, fill = country_us)) +
  geom_bar() +
  facet_wrap(~ category) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Number of laureates",
    title = "Living Nobel laureates: USA vs. Other"
  ) + 
     scale_fill_manual(values = c("Other" = "#6baed6", "USA" = "#fc8d62")) + 
  theme_minimal()
```
Make it more colorful
### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
